Sequence complexity

### 2011-07-02 article.tex
Started huge corrections

\title{Sequences complexity}
\author{Axel Schumacher\\Télécom ParisTech\\Free Project}
\date{\today}

@@

As a student at Télécom ParisTech, I chose to follow the 'Non-classic languages paradigms' course with Samuel Tardieu\cite{samuel}, while working on a free project with Jean-Louis Dessalles\cite{jld}.
Jean-Louis Dessalles suggested a project based on a Komolgorov's complexity problem: given a small sequence of digits, shapes or characters, I had to design a small program able to complete this list as well as an eight-years old children. \cite{starting_point}

The main goal of this project is to apply Kolmogorov theory on the given list in order to compress it in a optimal and human way, so that we will then be able to extend that list using found compression process.
On the 'Non-classic languages paradigms' course, we learned small spread languages as Haskel, Scala or Factor, and we were also supposed to perform a small implementation project using one of those languages.

@@

\section{Problematic}

>>>>

\title{Sequence complexity}
\author{Axel Schumacher\\Télécom ParisTech\\Free Project}
\date{\today}

@@

As a student at Télécom ParisTech, I chose to follow the 'Non-classical language paradigms' course with Samuel Tardieu\cite{samuel}, while working on a free project with Jean-Louis Dessalles\cite{jld}.
Jean-Louis Dessalles suggested a project based on a Komolgorov complexity problem: given a small sequence of digits, shapes or characters, I had to design a small program able to complete this list as well as an eight-year old child. \cite{starting_point}

The main goal of this project is to apply Kolmogorov theory to the given list in order to compress it in an optimal and human way.
This would then able us to extend that list using that compression.
During the "Non-classic language paradigms" course, we studied small spread languages as Haskel, Scala or Factor, and we were also supposed to perform a small implementation project using one of those languages.

@@

\section{Problem description}
